A novel distributed nature-inspired algorithm for solving optimization problems

### 2021-09-30 paper.tex
Final Updates
Section labels and references improvements

We present the description of the following sections in our paper. First, we
introduce our algorithm inspired by the Life-Cycle of animal species in section
2, followed by our experimental configuration and results in section 3, we
analyze and describe some of our research findings in section 4, and we
finalize by presenting some inferences based on our experiments' results in
section 5.

\section{Proposal}

@@

\section{Experiments}

@@

\section{Discussion}

@@

\section{Conclusions}

>>>>

We present the description of the following sections in our paper. First, we
introduce our algorithm inspired by the Life-Cycle of animal species in
section~\ref{proposal_section}, followed by our experimental configuration and
results in section~\ref{experiments_section}, we analyze and describe some of
our research findings in section~\ref{discussion_section}, and we finalize by
presenting some inferences based on our experiments' results in
section~\ref{conclusions_section}.

\section{Proposal}
\label{proposal_section}

@@

\section{Experiments} 
\label{experiments_section}

@@

\section{Discussion}
\label{discussion_section}

@@

\section{Conclusions}
\label{conclusions_section}
